### 2024-01-23 iterative_monomorphisation.tex
started considering potential bounds to explore

\begin{center}
\captionof{table}{Bounds and options to test}
\begin{tabular}{ccccc}
   \toprule
   \multicolumn{5}{c}{monomorphisation point (steps)} \\
   0 & 25 & 50 & 100 & 200 \\
   \midrule
   \multicolumn{4}{c}{new clauses multiplier} \\
   1.0 & 1.5 & 2.0 & 3.0 \\
   \midrule
   \multicolumn{3}{c}{total new clauses cap} \\
   2000 & 5000 & none\\
   \midrule
   \multicolumn{4}{c}{loop number} \\
   2 & 3 & 4 & 5 \\
   \midrule
   \multicolumn{5}{c}{monomorphisation point (steps)} \\
   0 & 25 & 50 & 100 & 200 \\

@@

>>>>

\begin{center}
\captionof{table}{Bounds and options to test}
\begin{tabular}{cccccc}
   \toprule
   \multicolumn{5}{c}{monomorphisation point (steps)} \\
   0 & 25 & 50 & 100 & (200) \\
   \midrule
   \multicolumn{4}{c}{new clauses multiplier} \\
   1.0 & 1.5 & 2.0 & (3.0) \\
   \midrule
   \multicolumn{3}{c}{total new clauses cap} \\
   2000 & 5000 & none\\
   \midrule
   \multicolumn{4}{c}{loop number} \\
   2 & 3 & 4 & 5 \\
   \midrule
   \multicolumn{5}{c}{monomorphisation point (steps)} \\
   0 & 25 & 50 & 100 & (200) \\
   \midrule
   \multicolumn{5}{c}{e-timeout} \\
   2.0 & 5.0 & 10.0 & 15.0 & no timeout \\
   \midrule
   \multicolumn{3}{c}{new poly ty arg limit per fun sym multiplier} \\
   0 & 0.5 & 1.0  \\
   \midrule
   \multicolumn{3}{c}{new poly ty arg limit per fun sym floor} \\
   0 & 2 & 5  \\
   \midrule
   \multicolumn{3}{c}{new poly ty arg limit per fun sym cap} \\
   10 & 20 & 50  \\
   \midrule
   \multicolumn{5}{c}{new mono ty arg limit per fun sym multiplier} \\
   0..5 & 1.0 & 1.5 & 2.0 & (3.0)\\
   \midrule
   \multicolumn{5}{c}{new mono ty arg limit per fun sym floor} \\
   0 & 2 & 5 & 7 & 10\\
   \midrule
   \multicolumn{4}{c}{new mono ty arg limit per fun sym cap} \\
   10 & 20 & 50 & 100  \\
   \midrule
   \multicolumn{3}{c}{monomorphising subst per clause} \\
   2 & 5 & 7  \\
   \midrule
   \multicolumn{5}{c}{subst per clause (total, split 50/50)} \\
   1000 & 2000 & 5000 & 10000 & 15000  \\

@@

We ignore the following bounds: ty var limit per clause, subst per ty var, limiting the new type args per clause
